SIRV-RL: Reinforcement Learning for Optimized Policy Control during Epidemiological Outbreaks in Emerging Market and Developing Economies

### 2024-01-11 paper_draft/main.tex
including trash, time varying nu model, changing the rl

\title{SIR-RL: Reinforcement Learning for Optimized Policy Control during Epidemiological Outbreaks in Emerging Market and Developing Economies}
\author[1,*]{Maeghal Jain}
\author[1]{Ziya Uddin}

@@

\subsection*{Methodology}
In SIR-RL, we use a compartmental model to model infectious disease. Here we divide people of the population, based on whether they are yet to come into contact with an infected person (Susceptible), are infectious themselves (Infectious), or have recovered from the infection (Recovered). These compartments create the SIR model which can be represented as follows:

@@

\subsection*{Results}
% https://www.nature.com/articles/s41598-020-79147-8 (see this to write results)
Using the simple SIR model (\ref{eq:S_without_lockdown}, ~\ref{eq:cost_without_lockdown}) to model the disease dynamics we get:
\begin{figure}[H]
  \centering
  \caption{SIR Model for India}
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\linewidth]{images/SIR_model_IND.eps}
    \caption{SIR model for India}
  \end{subfigure}
  \label{fig:SIR_model_IND}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.25]{images/SIR_model_infections_IND.eps}
    \caption{Infections modelled with SIR model}
  \end{subfigure}
  \label{fig:SIR_model_infections_IND}
\end{figure}

Combining the lockdown dynamics in the SIR model we get this following:
\begin{figure}[H]
  \centering
  \caption{SIR Model with lockdown for India}
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\linewidth]{images/SIR_model_with_lockdown_IND.eps}
    \caption{SIR model with lockdown}
  \end{subfigure}
  \label{fig:SIR_model_with_lockdown_IND}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.25]{images/SIR_model_with_lockdown_infections_IND.eps}
    \caption{Infections modelled with SIR model with Lockdown}
  \end{subfigure}
  \label{fig:SIR_model_with_lockdown_infections_IND}
\end{figure}

Combining vaccination dynamics with SIR with lockdown model we get the following:
\begin{figure}[H]
  \centering
  \caption{SIRV Model with lockdown for India}
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\linewidth]{images/SIRV_model_with_lockdown_IND.eps}
    \caption{SIRV model with lockdown}
  \end{subfigure}
  \label{fig:SIRV_model_with_lockdown_IND}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.25]{images/SIRV_model_with_lockdown_infections_IND.eps}
    \caption{Infections modelled with SIRV model with Lockdown}
  \end{subfigure}
  \label{fig:SIRV_model_with_lockdown_infections_IND}
\end{figure}

>>>>

\title{SIRV-RL: Reinforcement Learning for Optimized Policy Control during Epidemiological Outbreaks in Emerging Market and Developing Economies}
\author[1,*]{Maeghal Jain}
\author[1]{Ziya Uddin}

@@

\subsection*{Mathematical Formulation}
In SIR-RL, we use a compartmental model to model infectious disease. Here we divide people of the population, based on whether they are yet to come into contact with an infected person (Susceptible), are infectious themselves (Infectious), or have recovered from the infection (Recovered). These compartments create the SIR model which can be represented as follows:

@@

\subsection*{Results}
% https://www.nature.com/articles/s41598-020-79147-8 (see this to write results)
Using the simple SIR model (\ref{eq:S_without_lockdown}, ~\ref{eq:cost_without_lockdown}) to model the disease dynamics we get:
\begin{figure}[H]
  \centering
  \caption{SIR Model with lockdown for India}
  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.5]{images/SIR_model_IND.eps}
    \caption{SIR model with lockdown}
    \label{fig:SIR_mode_IND}
  \end{subfigure}
  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIR_model_infections_IND.eps}
    \caption{Infections modelled with SIR model}
    \label{fig:SIR_model_infections_IND}
  \end{subfigure}
\end{figure}

Combining the lockdown dynamics in the SIR model we get this following:
\begin{figure}[H]
  \centering
  \caption{SIR Model with lockdown for India}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIR_model_with_lockdown_IND.eps}
    \caption{SIR model with lockdown}
    \label{fig:SIR_model_with_lockdown_IND}
  \end{subfigure}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/stringency_varying_with_time_IND.eps}
    \caption{Stringency varying with Time}
    \label{fig:stringency_varying_with_time_IND}
  \end{subfigure}
\end{figure}
\begin{figure}[H]\ContinuedFloat
  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIR_model_with_lockdown_infections_IND.eps}
    \caption{Infections modelled with SIR model with Lockdown}
    \label{fig:SIR_model_with_lockdown_infections_IND}
  \end{subfigure}
\end{figure}

Combining vaccination dynamics with SIR with lockdown model we get the following:
\begin{figure}[H]
  \centering
  \caption{SIRV Model with lockdown for India}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIRV_model_with_lockdown_IND.eps}
    \caption{SIRV model with lockdown}
    \label{fig:SIRV_model_with_lockdown_IND}
  \end{subfigure}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIRV_model_with_lockdown_infections_IND.eps}
    \caption{Infections modelled with SIRV model with Lockdown}
    \label{fig:SIRV_model_with_lockdown_infections_IND}
  \end{subfigure}

\end{figure}

For time-varying $\nu$ we get the folllowing:
\begin{figure}[H]
  \centering
  \caption{SIRV Model with lockdown and time-varying $\nu$ for India}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIRV_model_with_lockdown_time_varying_nu_IND.eps}
    \caption{SIRV model with lockdown and time-varying $\nu$}
    \label{fig:SIRV_model_with_lockdown_time_varying_nu_IND}
  \end{subfigure}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \includegraphics[scale=0.50]{images/SIRV_model_with_lockdown_infections_time_varying_nu_IND.eps}
    \caption{Infections modelled with SIRV model with Lockdown and time-varying $\nu$}
    \label{fig:SIRV_model_with_lockdown_infections_time_varying_nu_IND}
  \end{subfigure}
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Loss for Different Models}
  \includegraphics[width=\linewidth]{images/comparing_costs_IND.eps}
  \label{fig:comparing_costs_IND}
\end{figure}
